Scattering from compact objects, Regge poles \\ and the Complex Angular Momentum method

### 2019-09-17 rainbowCAM.tex
blah

%\title{Off-axis plane wave scattering on rotating black holes}
\title{Scattering from compact objects: Regge poles and complex angular momentum}

@@

\section{Introduction}
 The topic of time-independent scattering has been studied in detail since the 1960s \cite{Hildreth1964PhDT64, Matzner:1968, Vishveshwara:1970}, and there now exists a substantial literature \cite{Mashhoon:1973zz,Chrzanowski:1976jb,DeLogi:1977dp,Sanchez:1977vz,MatznerRyan1978,Handler:1980un,Matzner:1985rjn,Futterman:1988ni,Andersson:1995vi,Glampedakis:2001cx,Dolan:2006vj,Dolan:2007ut,Dolan:2008kf,Crispino:2009xt,Cotaescu:2014jca,Sorge:2015yoa,Gussmann:2016mkp,Leite:2017zyb,Nambu:2019sqn, Folacci:2019vtt,Leite:2019eis}.

>>>>

\title{Scattering from compact objects, Regge poles \\ and the Complex Angular Momentum method}

@@

\section{Introduction}
Blah.

 The topic of time-independent scattering has been studied in detail since the 1960s \cite{Hildreth1964PhDT64, Matzner:1968, Vishveshwara:1970}, and there now exists a substantial literature \cite{Mashhoon:1973zz,Chrzanowski:1976jb,DeLogi:1977dp,Sanchez:1977vz,MatznerRyan1978,Handler:1980un,Matzner:1985rjn,Futterman:1988ni,Andersson:1995vi,Glampedakis:2001cx,Dolan:2006vj,Dolan:2007ut,Dolan:2008kf,Crispino:2009xt,Cotaescu:2014jca,Sorge:2015yoa,Gussmann:2016mkp,Leite:2017zyb,Nambu:2019sqn, Folacci:2019vtt,Leite:2019eis}.
